\vspace{-2.0cm} \textbf{Talking with body expressions} \\ \Large \textbf{A Method for detecting sings in a weakly annotated dataset}

### 2019-06-29 article/article-tesis.tex
abstract

\begin{abstract}
People with deafness or hearing disabilities are aimed to use computer based systems, state of art video classification and human action recognition rely in a combination of traditional and new methods like optical flow and 3D CNN. In this article we show a method to detect Peruvian Sign Language elements from a weakly annotated videos dataset. Video annotation techniques were applied increasing the models performance, as a result we achieved XX precision and XX exhaustiveness by training a 3D CNN with optical flow inputs.   \\
\keywords{video classification,human actions detection, optical flow, 3D CNN.}
\end{abstract}

>>>>

\begin{abstract}
People with deafness or hearing disabilities who aim to use computer based systems, state of art video classification and human action recognition rely in a combination of traditional and new methods like optical flow and 3D CNN. In this article we show a method to detect Peruvian Sign Language elements from a weakly annotated videos dataset. Video annotation techniques were applied increasing the models performance, as a result we achieved XX precision and XX exhaustiveness by training a 3D CNN with optical flow inputs.   \\
\keywords{video classification,human actions detection, optical flow, 3D CNN.}
\end{abstract}
